Notes on Validated Model Counting \\ Version of \today

### 2022-05-03 doc/mc-notes.tex
Improved explanations

\begin{table}
  \caption{Encodings of the ITE Operation}
  \label{tab:ite}
  \begin{center}
  \begin{tabular}{ccc}
    ITE Form & & Encoding \\
    \midrule
     $\ite(S_1, S_2, S_3)$ & $$ & $(S_1 \pand S_2) \por (\neg S_1 \land S_3)$ \\
     $\ite(\tautology, S_2, S_3)$ & $$ & $S_2$ \\
     $\ite(\nil, S_2, S_3)$ & $$ & $S_3$ \\
     $\ite(S_1, \tautology, \nil)$ & $$ & $S_1$ \\
     $\ite(S_1, \nil, \tautology)$ & $$ & $\neg S_1$ \\
     $\ite(S_1, S_2, \nil)$ & $$ & $S_1 \pand S_2$ \\
     $\ite(S_1, \nil, S_3)$ & $$ & $\neg S_1 \pand S_3$ \\
     $\ite(S_1, S_2, \tautology)$ & $$ & $\neg (S_1 \pand \neg S_2)$ \\
     $\ite(S_1, \tautology, S_3)$ & $$ & $\neg (\neg S_1 \pand \neg S_3)$ \\
  \end{tabular}
  \end{center}
\end{table}

Table~\ref{tab:ite} shows different ways to encode an ITE operation
into schema operations.  All of these require the dependency set of
the argument $S_1$ to be disjoint from those of arguments $S_2$ and
$S_3$.  The first row shows the most general case, require one $\por$
and two $\pand$ operations.  The other rows show special cases, where
one or more argument is a constant.  Of these, the final two rows are
particularly noteworthy.  They make use of DeMorgan's Laws to convert
disjunctions into conjunctions.  These conjunctions can then be
encoded with $\pand$ operations, since their arguments will have
disjoint dependency sets.

>>>>

\begin{table}
  \caption{Encodings of the ITE Operation}
  \label{tab:ite}
  \begin{center}
  \begin{tabular}{ccc}
    ITE Form & & Encoding \\
    \midrule
     $\ite(S_1, S_2, S_3)$ & $$ & $(S_1 \pand S_2) \por (\neg S_1 \land S_3)$ \\
     $\ite(\tautology, S_2, S_3)$ & $$ & $S_2$ \\
     $\ite(\nil, S_2, S_3)$ & $$ & $S_3$ \\
     $\ite(S_1, \tautology, \nil)$ & $$ & $S_1$ \\
     $\ite(S_1, \nil, \tautology)$ & $$ & $\neg S_1$ \\
     $\ite(S_1, S_2, \nil)$ & $$ & $S_1 \pand S_2$ \\
     $\ite(S_1, \nil, S_3)$ & $$ & $\neg S_1 \pand S_3$ \\
     $\ite(S_1, \tautology, S_3)$ & $$ & $\neg (\neg S_1 \pand \neg S_3)$ \\
     $\ite(S_1, S_2, \tautology)$ & $$ & $\neg (S_1 \pand \neg S_2)$ \\
  \end{tabular}
  \end{center}
\end{table}

Table~\ref{tab:ite} shows different ways to encode an ITE operation
into schema operations.  All of these require the dependency set of
the argument $S_1$ to be disjoint from those of arguments $S_2$ and
$S_3$.  The first row shows the most general case, requiring one
$\por$ and two $\pand$ operations.  The other rows show special cases,
where one or more argument is a constant.  Of these, the final two
rows are particularly noteworthy.  They make use of DeMorgan's Laws to
convert disjunctions into conjunctions.  In particular, for Boolean
functions $f_1$ and $f_2$, we can write $\ite(f_1, \tautology, f_2)$
as $f_1 \lor f_2$, and by DeMorgan's Laws as $\neg(\neg f_1 \land
\neg f_2)$.  Similarly $\ite(f_1, f_2, \tautology) = \neg f_1 \lor f_2 = \neg(f_1 \land \neg f_2)$.
These conjunctions can then be
encoded with $\pand$ operations, since their arguments will have
disjoint dependency sets.
